---
title: "Module2 R Markdown Doc 1"
author: "Donata Boretti"
date: "2024-07-01"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This is a level 1 header

## R Markdown

### This is a level 3 header

Here is an example of a non-numbered list:

* Breakfast
    - food
        + eggs
        + toast
        + bacon
    - drink
        + apple juice
* Lunch
    - taco


> Block quote
> Let's do a list
>
> 1. NestedOne
> 2. Two









Here there is a link to [GOOGLE](https://google.com)

Here is a word in **bold** and a word in __bold__.

Here is a word *italics* and _italics_.

When we compile our document, we are using the `R Markdown` package.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
